Visualization and analysis of probability distributions of large temporal data

### 2021-11-19 Rmd/04-gracsr.Rmd
Fig 4.8 caption

```{r opt-cluster-tsne-jsd, fig.cap = "Clustering summaries: (a) t-SNE computed on the $24$ selected customers, and (b) separation index (*sindex*) for $2$-$10$ clusters using JS-NQT, JS-RS and WPD. Various choices in number of clusters would be recommended. Four clusters are visible in t-SNE, although it might hide a fifth cluster because dimension reduction to 2D may be insufficient to see the difference. JS-NQT suggests $3$, JS-RS suggests $2$ or $5$ and WPD suggests $3$ or $5$."}
#include_graphics("img/opt_clust_parenthesis.png")
```

>>>>

(ref:opt-cluster-tsne-jsd) Clustering summaries: (a) t-SNE computed on the $24$ selected customers, and (b) separation index (*sindex*) for $2$-$10$ clusters using JS-NQT, JS-RS and WPD. Various choices in number of clusters would be recommended. Four clusters are visible in t-SNE, although it might hide a fifth cluster because dimension reduction to 2D may be insufficient to see the difference. JS-NQT suggests $3$, JS-RS suggests $2$ or $5$ and WPD suggests $3$ or $5$.

```{r opt-cluster-tsne-jsd, fig.cap = "(ref:opt-cluster-tsne-jsd)"}
#include_graphics("img/opt_clust_parenthesis.png")
```
